Install packages
```{r}
install.packages("tidyverse")
```
Load packages
```{r}
library("tidyverse")
```
Importing dataset
```{r}
Data <- read.csv("Data.csv")
```
Splitting data by treatment 
```{r}
Data.0tsp <- Data[c(1,2,9,10,17,18),]
Data.0.5tsp <- Data[c(3,4,11,12,19,20),]
Data.1tsp <- Data[c(5,6,13,14,21,22),]
Data.1.5tsp <- Data[c(7,8,15,16,23,24),]
```
Interactive Model
```{r}
fertlm <- lm(nitrate~Time*Fertilizer, data = Data)
summary(fertlm)
```
Finding & plotting linear regression for 0 tsp/control
```{r}
trt.0.lm <- lm(nitrate ~ Time, data = Data.0tsp)
summary(trt.0.lm)

Data.0tsp.nitrate.Time <- ggplot(data = Data.0tsp, aes(x = Time, y = nitrate)) + geom_point() + geom_smooth(method = "lm")  
Data.0tsp.nitrate.Time <- Data.0tsp.nitrate.Time + xlab("Time (days)") + ylab("nitrate (ppm)")
Data.0tsp.nitrate.Time
```
Finding & plotting linear regression for 0.5 tsp/control
```{r}
trt.0.5.lm <- lm(nitrate ~ Time, data = Data.0.5tsp)
summary(trt.0.5.lm)

Data.0.5tsp.nitrate.Time <- ggplot(data = Data.0.5tsp, aes(x = Time, y = nitrate)) + geom_point() + geom_smooth(method = "lm")
Data.0.5tsp.nitrate.Time <- Data.0.5tsp.nitrate.Time + xlab("Time (days)") + ylab("nitrate (ppm)")
Data.0.5tsp.nitrate.Time
```
Finding & plotting linear regression for 1 tsp/control
```{r}
trt.1.lm <- lm(nitrate ~ Time, data = Data.1tsp)
summary(trt.1.lm)

Data.1tsp.nitrate.Time <- ggplot(data = Data.1tsp, aes(x = Time, y = nitrate)) + geom_point() + geom_smooth(method = "lm")
Data.1tsp.nitrate.Time <- Data.1tsp.nitrate.Time + xlab("Time (days)") + ylab("nitrate (ppm)")
Data.1tsp.nitrate.Time
```
Finding & plotting linear regression for 1.5 tsp/control
```{r}
trt.1.5.lm <- lm(nitrate ~ Time, data = Data.1.5tsp)
summary(trt.1.5.lm)

Data.1.5tsp.nitrate.Time <- ggplot(data = Data.1.5tsp, aes(x = Time, y = nitrate)) + geom_point() + geom_smooth(method = "lm")
Data.1.5tsp.nitrate.Time <- Data.1.5tsp.nitrate.Time + xlab("Time (days)") + ylab("nitrate (ppm)")
Data.1.5tsp.nitrate.Time
```
Changing Fertilizer to a factor 
```{r}
Data.Treatment <- Data[, "Fertilizer"]
Data.Treatment.factor <- as.factor(Data.Treatment)
Data.minus <- Data[,-c(5)]
Data.minus$Treatment <- Data.Treatment.factor
```
Plotting the different treatments/ multiple regression line
```{r}
Data.fin <- ggplot(data = Data.minus, aes(x = Time, y = nitrate, group = Treatment, color = Treatment)) + geom_point() + geom_smooth(method = "lm") 
Data.fin <- Data.fin + xlab("Time (days)") + ylab("Nitrate (ppm)") + ggtitle("Effect of Fertilizer on Nitrate Levels Over Time")
Data.fin
```
Plotting mult line graph
```{r}
Data.fin <- ggplot(data = Data.minus, mapping = aes(x = Time, y = nitrate, group = Treatment, color = Treatment)) + geom_line() 
Data.fin <- Data.fin + xlab("Time (days)") + ylab("Nitrate (ppm)") + ggtitle("Effect of Fertilizer on Nitrate Over Time") + scale_fill_discrete(name = "Treatment(tsp)") 
Data.fin

```