
Install packages 
```{r}
install.packages("tidyverse")
```
Load packages
```{r}
library("tidyverse")
```

Importing dataset 
```{r}
Data <- read.csv("Data.csv")

```
Splitting data by treatment 
```{r}
Data.0tsp <- Data[c(1,2,9,10,17,18),]
Data.0.5tsp <- Data[c(3,4,11,12,19,20),]
Data.1tsp <- Data[c(5,6,13,14,21,22),]
Data.1.5tsp <- Data[c(7,8,15,16,23,24),]
```
Interactive Model
```{r}
fertlm <- lm(TDS~Time*Fertilizer, data = Data)
summary(fertlm)
```
Finding & plotting linear regression for 0 tsp/control
```{r}
trt.0.lm <- lm(TDS ~ Time, data = Data.0tsp)
summary(trt.0.lm)

Data.0tsp.TDS.Time <- ggplot(data = Data.0tsp, aes(x = Time, y = TDS)) + geom_point() + geom_smooth(method = "lm")
Data.0tsp.TDS.Time
```
Finding & plotting linear regression for 0.5 tsp
```{r}
trt.0.5.lm <- lm(TDS ~ Time, data = Data.0.5tsp)
summary(trt.0.5.lm)

Data.0.5tsp.TDS.Time <- ggplot(data = Data.0.5tsp, aes(x = Time, y = TDS)) + geom_point() + geom_smooth(method = "lm")
Data.0.5tsp.TDS.Time
```
Finding & plotting linear regression for 1 tsp
```{r}
trt.1.lm <- lm(TDS ~ Time, data = Data.1tsp)
summary(trt.1.lm)

Data.1tsp.TDS.Time <- ggplot(data = Data.1tsp, aes(x = Time, y = TDS)) + geom_point() + geom_smooth(method = "lm")
Data.1tsp.TDS.Time
```
Finding & plotting linear regression for 1.5 tsp
```{r}
trt.1.5.lm <- lm(TDS ~ Time, data = Data.1.5tsp)
summary(trt.1.5.lm)

Data.1.5tsp.TDS.Time <- ggplot(data = Data.1.5tsp, aes(x = Time, y = TDS)) + geom_point() + geom_smooth(method = "lm")
Data.1.5tsp.TDS.Time
```
Changing Fertilizer to a factor 
```{r}
Data.Treatment <- Data[, "Fertilizer"]
Data.Treatment.factor <- as.factor(Data.Treatment)
Data.minus <- Data[,-c(5)]
Data.minus$Treatment <- Data.Treatment.factor

```
Plotting the different treatments/ multiple regression line
```{r}
Data.fin <- ggplot(data = Data.minus, aes(x = Time, y = TDS, group = Treatment, color = Treatment)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Effect of Fertilizer on TDS Over Time")
Data.fin <- Data.fin + xlab("Time (days)") + ylab("TDS (ppm)")
Data.fin

```

